Concurrent Programming with CXL

### 2020-06-14 book/paper.tex
Latest

\chapter{List of CXL Values}

@@

\chapter{List of CXL Operators}

@@

\chapter{List of CXL Statements}

@@

\chapter{List of CXL Machine Instructions}

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
Address & compute address \\
\hline
Apply & pop $m$ and $i$ and apply $i$ to $m$, pushing a value \\
\hline
Assert & pop $b$ and check that it is \texttt{True} \\
\hline
AtomicDec & decrement the atomic counter of this context \\
\hline
AtomicInc & increment the atomic counter of this context \\
\hline
Choose & choose an element from the set on top of the stack \\
\hline
Del & delete a shared variable \\
\hline
DelVar $v$ & delete process variable $v$ \\
\hline
Dict & pop $n$ and $n$ key/value pairs and push a dictionary \\
\hline
Dup & duplicate the top element of the stack \\
\hline
Frame $m$ $a$ $r$& start method $m$ with arguments $a$,
initializing variables.  Last instruction is at $r$ \\
\hline
Go & restore context \\
\hline
JumpCond $e$ $p$ & pop expression and if equal to $e$ set program counter to $p$ \\
\hline
Jump $p$ & set program counter to $p$ \\
\hline
Load & load a shared variable and push it onto the stack \\
\hline
LoadVar $v$ & load process variable $v$ and push it onto the stack \\
\hline
Nary \textit{op} $n$ & apply $n$-ary operator \textit{op} to the top $n$ elements on the stack \\
\hline
Pop & pop a value of the stack and discard it \\
\hline
Push $c$ & push constant $c$ onto the stack \\
\hline
PushAddress $v$ & push the address of shared variable $v$ \\
\hline
Return & pop return address, push \texttt{result}, and restore program counter \\
\hline
Set & pop $n$ and $n$ elements and push a set of the elements \\
\hline
Spawn & pop tag, argument, and method and spawn a new context \\
\hline
Split & split a non-empty set in its minimum element and its remainder \\
\hline
Stop & save context \\
\hline
Store & pop a value from the stack and store it in a shared variable \\
\hline
StoreVar $v$ & pop a value from the stack and store it in process variable $v$ \\
\hline
\end{tabular}

>>>>

\chapter{List of Values}

@@

\chapter{List of Operators}

@@

\chapter{List of Statements}

@@

\chapter{List of Machine Instructions}

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
Address & compute address \\
\hline
Apply & pop $m$ and $i$ and apply $i$ to $m$, pushing a value \\
\hline
Assert & pop $b$ and check that it is \texttt{True} \\
\hline
AtomicInc & increment the atomic counter of this context \\
\hline
AtomicDec & decrement the atomic counter of this context \\
\hline
Choose & choose an element from the set on top of the stack \\
\hline
Del & delete a shared variable \\
\hline
DelVar $v$ & delete process variable $v$ \\
\hline
Dict & pop $n$ and $n$ key/value pairs and push a dictionary \\
\hline
Dup & duplicate the top element of the stack \\
\hline
Frame $m$ $a$ $r$& start method $m$ with arguments $a$,
initializing variables.  Last instruction is at $r$ \\
\hline
Go & pop context and value, push value on context's stack, and add to context bag \\
\hline
Jump $p$ & set program counter to $p$ \\
\hline
JumpCond $e$ $p$ & pop expression and, if equal to $e$, set program counter to $p$ \\
\hline
Load & load a shared variable and push it onto the stack \\
\hline
LoadVar $v$ & load process variable $v$ and push it onto the stack \\
\hline
Nary \textit{op} $n$ & apply $n$-ary operator \textit{op} to the top $n$ elements on the stack \\
\hline
Pop & pop a value of the stack and discard it \\
\hline
Push $c$ & push constant $c$ onto the stack \\
\hline
PushAddress $v$ & push the address of shared variable $v$ \\
\hline
Return & pop return address, push \texttt{result}, and restore program counter \\
\hline
Set & pop $n$ and $n$ elements and push a set of the elements \\
\hline
Spawn & pop tag, argument, and method and spawn a new context \\
\hline
Split & pop set and push minimum and remainder \\
\hline
Stop & save context into shared variable and remove from context bag \\
\hline
Store & pop a value from the stack and store it in a shared variable \\
\hline
StoreVar $v$ & pop a value from the stack and store it in process variable $v$ \\
\hline
\end{tabular}
\vspace{1em}

Clarifications:
\begin{itemize}
\item The effect of the \texttt{Apply} instructions depends much on $m$.
If $m$ is a dictionary, then \texttt{Apply} finds $i$ in the dictionary
and pushes the value.
If $m$ is a program counter, then \texttt{Apply} invokes method $m$ by
pushing the current program counter and setting the program counter to
$m$.  $m$ is supposed to leave the result on the stack.
\end{itemize}
